%-------------------------
% Resume in Latex
% Author : Steven Jessup
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize #1} & \normalsize #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize #1} & \normalsize #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
   
\begin{center}
    \vspace{2pt}
    \textbf{\Huge \scshape Steven Jessup} \\ \vspace{1pt}
    \vspace{3pt}
    \small 209-302-5813 $|$ 
    \href{https://stevenjessup.com}{www.stevenjessup.com} $|$
    \href{mailto:me@stevenjessup.com}{me@stevenjessup.com} $|$ 
    \href{https://linkedin.com/in/jessupsteven}{linkedin.com/in/jessupsteven} $|$
    \href{https://github.com/jessupthefish}{github.com/jessupthefish} 
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \vspace{2pt}
    \resumeSubheading
      {Code Ninjas $|$ Center Director}{July 2023 -- April 2024}
      \resumeItemListStart
        \resumeItem{Instructed students in programming languages such as JavaScript, Python, and C\#, focusing on building foundational skills in coding and problem-solving.}
        \resumeItem{Led and taught game modding clubs, including Minecraft and Roblox, helping students create custom game content while learning coding principles and problem-solving skills.}
        \resumeItem{Designed and implemented a dynamic coding curriculum tailored to various learning styles and experience levels, resulting in improved student engagement and comprehension.}
      \resumeItemListEnd

    \resumeSubheading
      {US Navy $|$ Fire Controlman First Class}{July 2013 -- Aug. 2021}
      
      \resumeSubSubheading
        {Commander, Naval Forces Japan}{}
        \resumeItemListStart
        \resumeItem{Utilized the Global Command and Control System - Maritime (GCCS-M) to manage critical information and communications in support of operational planning and decision-making.}
        \resumeItem{Collaborated with higher echelons and the Japan Maritime Self-Defense Force, delivering over 300 intelligence products on schedule, supporting mission readiness and operational success.}
        \resumeItemListEnd

      \resumeSubSubheading
        {Surface Development Squadron One}{}
        \resumeItemListStart
          \resumeItem{Delivered IT support and maintained over 1,000 NMCI accounts via the NMCI Enterprise Tools Database.}
          \resumeItem{Resolved high-priority network and hardware issues, ensuring uninterrupted operations across 15+ naval units, achieving a 99\% system uptime.}
        \resumeItemListEnd

      \resumeSubSubheading
        {Commander, Seventh Fleet}{}
        \resumeItemListStart
          \resumeItem{Led a team of 20 in planning and executing 106 multinational Tomahawk strike missions through the Mission Distribution System (MDS) for creation, distribution, and execution. Earned the highest assessed tactical proficiency for two consecutive years.}
          \resumeItem{Troubleshot and maintained classified data links via SHF SATCOM, ensuring secure communication for over 200 high-priority missions, maintaining 100\% operational integrity.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


  %-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Java, JavaScript, Python, HTML/CSS} \\
         \vspace{2pt}
     \textbf{Tools \& Platforms}{: React, Node.js, Express, Git, GitHub, Linux, Windows, Mac, CMake, VS Code} \\
    }}
 \end{itemize}
 
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{IT Ticketing System} $|$ \emph{JavaScript, React, Node.js, Express, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Built a full-stack ticketing system enabling users to submit and track support requests through a React-based interface and Express API.}
            \resumeItem{Designed and implemented a PostgreSQL schema to store ticket data with fields for title, description, priority, status, and timestamps.}
            \resumeItem{Integrated secure form handling and real-time ticket creation with client-server communication using RESTful endpoints.}
            \resumeItem{Developed admin dashboard functionality to view, edit, and delete tickets, with role-based feature separation.}
            \resumeItem{Implemented data validation and error handling across frontend and backend layers to ensure system reliability.}
             \resumeItem{Enhanced code organization by separating routes, database logic, and components for easier maintainability and scaling.}
             \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{VG Archive} $|$ \emph{C++, Python, SQLite, SQL, CMake}}{}
          \resumeItemListStart
            \resumeItem{Developed a video game archive application in C++ with a SQLite backend, featuring a CLI for full CRUD operations.}
            \resumeItem{Designed a relational database schema to manage titles, genres, release dates, and ratings, and integrated Python-based API scraping to enrich records.}
            \resumeItem{Implemented custom SQL queries for dynamic filtering and built CMake-based tooling for streamlined compilation and cross-platform support.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {California State University, East Bay}{Expected Graduation: May 2026}
      {Bachelor of Science in Computer Science}{Hayward, CA}
\resumeSubHeadingListEnd 
\end{document}
